\maketitle
\makedeclaration

\begin{abstract} % 300 word limit
We consider in RTB display advertising how advertisers actively bid an impression considering a long-term objective. It is a combination of CTR estimation and repeated auctions. First, we use the CTR prediction models to find the distribution of market price estimator and then we deal with a reinforcement learning problem to maximise the total utility during the finite sequential auctions. Three CTR prediction models are applied here to obtain the estimator. FFM usually has the better performance than BOPR and FTRL. The ensemble of these three predictors can lead to more effective performance. Our analysis shows that in the second price auction with a logistic click-through model, the optimal bid strategy is not to bid the true value but bid a higher price than it in a finite sequential process. In the end, after advertisers obtain enough information and feedbacks from the market, the bidding price will converge to their true value and it becomes a one-shot auction with side information.
\end{abstract}

\begin{acknowledgements}
First and foremost I would like to sincerely thank my project supervisor Dr. Jun Wang who always had time for me. Without his invaluable advice, guidance and supervision, the quality of this thesis cannot reach such high satisfaction. I appreciate the wisdom of his way in both technical and theoretical perspectives that motivated me to think forward and concentrate on my project deeply. His academic rigor, enthusiasm and strong sense of responsibility are the most valuable characters I learnt during the period. Besides, I really want to thank PhD student and also my good friend Weinan Zhang who gave me many useful suggestions for the project. His patience and professional skills left me an unforgettable impression. I would also like to thank my personal tutor Dr. Massimiliano Pontil for his tutorials throughout my entire MSc course. Most of all, heartfelt thanks must go to my parents and my family. They have offered me unconditional support and encouragement since I went to master study at UCL. Thank for their company through both the highs and lows of my experience. They are the most important and wonderful treasure in my life forever.
\end{acknowledgements}

\setcounter{tocdepth}{2} 
% Setting this higher means you get contents entries for
%  more minor section headers.

\tableofcontents
\listoffigures
\listoftables

